### 2014-01-14 manuscripts/dpp-msbayes/dpp-msbayes-tables.tex
More work on model tables for dpp manuscript.

        \bottleScalar{}{}, and one \bottleTime{} parameters.

@@

        \globalcoalunit generations and millions of generations ago (MGA), the
        latter assuming a per-site rate of 1\e{-8} mutations per generation.

>>>>

        \bottleScalar{}{}, and one \bottleTime{} parameter.

@@

        \globalcoalunit generations followed in brackets by units of millions
        of generations ago (MGA), with the former converted to the latter
        assuming a per-site rate of 1\e{-8} mutations per generation.
